Detecting social information in a dense dataset of infants’ natural visual experience

### 2020-01-24 paper/cogsci/paper.Rmd
fix references

# Introduction
Infants are confronted by a blooming, buzzing onslaught of stimuli [@James1981] which they must learn to parse to make sense of the world around them. Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs. averted gaze [@Farroni2002], despite their limited acuity. As faces are likely to be an important conduit of social information that scaffolds cognitive development, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.

Yet until recently most hypotheses about infants’ visual experience have gone untested. Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008). By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world. Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].

As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied. Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @Franchak papers] as well as different view of objects [@Soska2010].  Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016]. In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@YuSmith2013].

Here, we analyze the social information present in the infant visual perspective by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam]. In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of contexts, encompassing infants’ viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).  Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective. Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@YoshidaSmith2008, @SmithFausey-Review] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.

@@

```
As has been observed in other studies on automated annotation of headcam data [e.g. @frank2013, @REF-chenyu-hand-paper], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion. For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.

@@

```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces vs. hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B). Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range."}

>>>>

# Introduction
Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] which they must learn to parse to make sense of the world around them. Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@gredeback2008microstructure], and even newborns prefer to look at faces with direct vs. averted gaze [@Farroni2002], despite their limited acuity. As faces are likely to be an important conduit of social information that scaffolds cognitive development, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.

Yet until recently most hypotheses about infants’ visual experience have gone untested. Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011]. By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world. Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].

As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied. Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not]. Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016]. In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@yu2013joint].

Here, we analyze the social information present in the infant visual perspective by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam]. In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of contexts, encompassing infants’ viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).  Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective. Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@yoshida2008, @smith2015contributions] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.

@@

```
As has been observed in other studies on automated annotation of headcam data [e.g. @frank2013, @sanchez2018postural, @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion. For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.

@@

```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces (A), hands (B), and faces vs. hands (C) in the entire dataset and (D). when hand detections are restricted to the upper 60 percent of the field of view (B). Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}
